Developing a Bubble Chamber Particle Discriminator Using Semi-Supervised Learning

### 2018-11-20 documentation/paper.tex
Clarified WIMP search runs

    \begin{enumerate}
        \item Neutron calibration sets, which are known to contain approximately 90\% neutrons, and
        \item Background radiation runs, which contain approximately 99\% alpha particles
    \end{enumerate}
\end{enumerate}

@@

Beyond this, the banded Fourier transform $\beta_{8}$ (which is the input to the AP function and the original machine learning analysis) was computed by integrating the resonant energy over all frequencies within each of a set of bands. This can be thought of as a method of signal downscaling, compressing the information into a smaller number of data points.

>>>>

    \begin{enumerate}
        \item Neutron calibration sets, which are known to contain approximately 90\% neutrons, and
        \item WIMP search runs, which contain approximately 99\% alpha particles
    \end{enumerate}
\end{enumerate}

@@

Beyond this, the banded Fourier transform $\beta_{8}$ (which is the input to the AP function and the original machine learning analysis) was computed by integrating the resonant energy over all frequencies within each of a set of frequency bands ranging from 1 kHz to 300 kHz \cite{pico}. This can be thought of as a method of signal downscaling, compressing the information into a smaller number of data points.
